Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-16 prop_letter.tex
prop_letter.tex Update citations...

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome
of a theory that is contextual depends upon
whether  compatible sets of observables are measured together or
separately; a non-contextual theory gives the same results in either
case.  A classic example of the varying opinions on the impact of
imprecision is the disagreement between
Meyer~\cite{PhysRevLett.83.3751} and 
Mermin~\cite{Mermin1999}  on whether finite-precision
measurements invalidate the spirit of the Kochen-Specker
theorem~\cite{kochenspecker1967,peres1995quantum}.  The Kochen-Specker  
theorem is in essence a
mathematical statement about contextuality, asserting that
in a Hilbert space of dimension $d \ge 3$, it is
impossible to associate definite measured values, $\mu(P_i)= 0$ or
$1$, with every projection operator~$P_i$, in such a way that, if a
set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$.   Meyer showed that one {\it can\/}
assign definite values $0$ or $1$ to the measurement outcome
$\mu(P_i)$ when the Hilbert space is defined over the field of
rational numbers, therefore nullifying the
theorem~\citep{PhysRevLett.83.3751}.  However, Mermin then argued
that measurement outcomes must depend smoothly on slight changes in
the experimental configuration, leading him to assert that the
impact of Meyer's negative result is
``unsupportable''~\citep{Mermin1999}.  The debate on
whether contextuality is consistent with experimental
outcomes continues to be an active topic of research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

>>>>

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome
of a theory that is contextual depends upon
whether  compatible sets of observables are measured together or
separately; a non-contextual theory gives the same results in either
case.  A classic example of the varying opinions on the impact of
imprecision is the disagreement between
Meyer~\cite{PhysRevLett.83.3751} and 
Mermin~\cite{Mermin1999}  on whether finite-precision
measurements invalidate the spirit of the Kochen-Specker
theorem~\cite{kochenspecker1967,peres1995quantum}.  The Kochen-Specker  
theorem is in essence a
mathematical statement about contextuality, asserting that
in a Hilbert space of dimension $d \ge 3$, it is
impossible to associate definite measured values, $\mu(P_i)= 0$ or
$1$, with every projection operator~$P_i$, in such a way that, if a
set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$.   Meyer showed that one {\it can\/}
assign definite values $0$ or $1$ to the measurement outcome
$\mu(P_i)$ when the Hilbert space is defined over the field of
rational numbers, therefore nullifying the
theorem~\citep{PhysRevLett.83.3751}.  However, Mermin then argued
that measurement outcomes must depend smoothly on slight changes in
the experimental configuration, leading him to assert that the
impact of Meyer's negative result is
``unsupportable''~\citep{Mermin1999}.  The debate on
whether contextuality is consistent with experimental
outcomes continues to be an active topic of research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
